Arcturus: efficient proofs for confidential transactions

### 2020-09-18 paper/iacr.tex
Minor paper updates

We claim that the protocol is $(m+1)$-special sound, where $m > 1$.
To show this, we construct an extractor that, when given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness for the statement.
In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define aggregation coefficients $\mu_k$ as before:
\begin{multline*}
\mathcal{R}' \equiv \Bigg\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sumu \mu_{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu_{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu_{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
\end{multline*}
Observe that if we assume that the dual-target discrete logarithm problem is hard in $\G$, extraction of a witness for $\mathcal{R}'$ implies knowledge of a corresponding witness for $\mathcal{R}$; this in turn provides the desired soundness.

@@

These terms are used to form a statement using the relation $\mathcal{R}$.
The user generates a proof showing the validity of this statement with the corresponding secret values as a witness set; the proof demonstrates knowledge of the signing keys $\{r^{(u)}\}_{u=0}^{w-1}$, and the witness $y$ formed by the commitment differences demonstrates that the input and output values balance.
Provided the commitment scheme used for value representation is (at least computationally) binding, the user cannot produce such a value $y$ unless the values balance correctly; in our case, Pedersen commitments satisfy this requirement.

We call the elements of the set $\{J^{(u)}\}_{u=0}^{w-1}$ the \textit{linking tags} for the transaction.
Similar to their use in linkable ring signatures, they are used by the verifier to detect attempts to sign with a secret key multiple times, either within the same transaction or between multiple transactions.
The construction $J^{(u)} = (r^{(u)})^{-1}U$ is an injective one-way verifiable random function \cite{dodis} using the secret key $r^{(u)}$; if the verifier sees the same linking tag used elsewhere, it knows that the (unknown) secret key was used again.
In our confidential transaction model, this corresponds to an attempt to double-spend funds that would be rejected by the verifier.

>>>>

We claim that the protocol is $(m+1)$-special sound, where $m > 1$.
To show this, we construct an extractor that, when given $m+1$ valid responses to $m+1$ distinct verifier challenges for the same initial statement, produces a valid witness for the statement.
In particular, we produce a modified witness for the following relation that is based on the information presented in the prover algorithm, where we define aggregation coefficients $\mu_k$ as before:
\begin{multline*}
\mathcal{R}' \equiv \Bigg\{ \{M_k\}_{k=0}^{N-1},\{P_k\}_{k=0}^{N-1},\{J^{(u)}\}_{u=0}^{w-1},\{Q_j\}_{j=0}^{T-1} \subset \G \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, y \right) : \\
\sumu \mu_{l^{(u)}} M_{l^{(u)}} = \sumu \mu_{l^{(u)}} r^{(u)}G \text{ and } \sumu \mu_{l^{(u)}} r^{(u)}J^{(u)} = \sumu \mu_{l^{(u)}} U \text{ and } \sum_{u=0}^{w-1} P_{l^{(u)}} - \sum_{j=0}^{T-1} Q_j = yG \Bigg\}
\end{multline*}
Observe that if we assume that the dual-target discrete logarithm problem is hard in $\G$ and $\hs$ is modeled as a random oracle, a witness for $\mathcal{R}'$ produced by the extractor must also be a witness for $\mathcal{R}$ using the same statement.
This means that extraction of a witness for $\mathcal{R}'$ is sufficient to establish the desired soundness.

@@

These terms are used to form a statement tuple for the relation $\mathcal{R}$:
$$\left( \{M_i\}_{i=0}^{N-1}, \{P_i\}_{i=0}^{N-1}, \{(r^{(u)})^{-1}U\}_{u=0}^{w-1}, \{Q_j\}_{j=0}^{T-1} \: ; \: \left( \{l^{(u)}\}_{u=0}^{w-1}, \{r^{(u)}\}_{u=0}^{w-1}, \sumu a_{l^{(u)}} - \sum_{j=0}^{T-1} b_j \right) \right)$$
The user generates a proof showing the validity of this statement with the corresponding secret values as a witness set; the proof demonstrates knowledge of the signing keys $\{r^{(u)}\}_{u=0}^{w-1}$, and the witness $y$ formed by the commitment differences demonstrates that the input and output values balance.
Provided the commitment scheme used for value representation is (at least computationally) binding, the user cannot produce such a value $y$ unless the values balance correctly; in our case, Pedersen commitments satisfy this requirement.

We call the elements of the set $\{J^{(u)}\}_{u=0}^{w-1}$ the \textit{linking tags} for the transaction.
Similar to their use in linkable ring signatures, they are used by the verifier to detect attempts to sign with a secret key multiple times, either within the same transaction or between multiple transactions.
The map $r^{(u)} \mapsto J^{(u)} \equiv (r^{(u)})^{-1}U$ is an injective one-way pseudorandom function \cite{dodis}; if the verifier sees the same linking tag used elsewhere, it knows that the (unknown) secret key was used again.
In our confidential transaction model, this corresponds to an attempt to double-spend funds that would be rejected by the verifier.
